Brownian dynamics simulation of cytoplasmic dynein's powerstroke reproduces bidirectional stepping

### 2020-08-13 papers/paper/paper.tex
Make papers/paper/paper.pdf build on Bennet from a fresh dynein_walk clone. Needed to add amsmath and graphicx packages. Not sure how this was building before??
add TODO stuff to paper

\usepackage{subcaption}
\usepackage{breqn}
\usepackage{color}

@@

>>>>

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{breqn}
\usepackage{color}

@@

\section*{TODO August 2020}
\begin{enumerate}
  \item Get new simulations working !!!!!!!!!!!!!!!!!!!
  \item Articulate data we fit to
  \begin{enumerate}
    \item Velocity -> unbinding rate
    \item Ratio of leading vs trailing steps -> exponential parameter
    \item Average step length -> other parameters
    \item Yildiz weird slope -> sticky rate + binding rate
    \item Avoid instant rebinds -> sticky rate
    \item Time to kick from MD??
    \item efficiency (affects instant rebind)
  \end{enumerate}
  \item Do the fit (requires 1 above)
  \item Could have a fixed binding immunity time rather than sticky rate
  \paragraph{Advantages of immunity time}
  \begin{enumerate}
    \item Might accurately reflect a diffusive escape from an energy well
  \end{enumerate}
  \paragraph{Advantages of sticky rate}
  \begin{enumerate}
    \item Accurately reflects the dynamics of a chemical process
  \end{enumerate}
\end{enumerate}
